A-maze: Easier measurement of incremental processing

### 2020-05-28 Papers/lab_meeting_2020.tex
more slides

\begin{itemize}
	\item Model the target sentence word by word \pause
	\item At each position, choose a high surprisal word
\end{itemize}
\medskip
\pause
Want quality control on distractors
\pause
\begin{itemize}
	\item Restrict to a list of possible distractors \pause
	\item Only consider distractors of same length, frequency as target word \pause
	\item Check distractors until we find one with high surprisal \pause
\end{itemize}

@@

\begin{frame}{Does A-maze work? }

Test it on materials from Witzel et al. (2012)
\medskip

Try with two pre-trained LSTM models (Gulordava 2018, Jozefowicz 2016)

@@

\begin{frame}{Caveats}
A lot of mistakes on the second word of the sentence ("The \ul{dog} ...") \pause
\includegraphics{../graph_errors2.pdf} \pause
Bad participants or bad distractors?

@@

\begin{frame}{Use A-maze!}
Easy to use! \pause
\begin{itemize}
	\item Runs on command line \pause
	\item Match distractors across minimal pair sentences \pause
	\item Customize surprisal thresholds, vocabulary lists \pause
	\item Can output pre-formatted for Ibex
\end{itemize}
\medskip
\pause
\end{frame}

@@

>>>>

\begin{itemize}
	\item Model the target sentence word by word \pause
	\item At each position, choose a high surprisal word
\end{itemize}
\medskip
\pause
Want quality control on distractors
\pause
\begin{itemize}
	\item Restrict to a list of possible distractors \pause
	\item Only consider distractors of same length, frequency as target word \pause
	\item Check distractors until we find one with high surprisal
\end{itemize}

@@

\begin{frame}{Does A-maze work? }
\pause
Test it on materials from Witzel et al. (2012)
\medskip

\pause
Try with two pre-trained LSTM models (Gulordava 2018, Jozefowicz 2016)

@@

\begin{frame}{Caveats}
A lot of mistakes on the second word of the sentence ("The \ul{dog} ...") \pause
\includegraphics{graph_errors2.pdf} \pause
Bad participants or bad distractors?

@@

\begin{frame}{Use A-maze!}
Easy to use! \pause
\begin{itemize}
	\item Runs on command line \pause
	\item Match distractors across minimal pair sentences \pause
	\item Customize surprisal thresholds, vocabulary lists \pause
	\item Can output pre-formatted for Ibex
\end{itemize}
\medskip
\end{frame}

@@

\begin{frame}{Regression coefficients}
\begin{tiny}
\begin{tabular}{l|rlr|rlr|rlr}
	\hline
	&\multicolumn{3}{c|}{5-gram}&\multicolumn{3}{c|}{GRNN}&\multicolumn{3}{c}{TXL}\\
	& Est & CI & $p$ & Est & CI & $p$ &Est & CI & $p$ \\ 
	\hline
	Intercept & 865.3 & [829.9, 902.9] & 0.00 & 871.1 & [837.9, 905.3] & 0.00 & 870.8 & [832.5, 907.8] & 0.00 \\ 
	Surprisal & 11.7 & [9.3, 14.1] & 0.00 & 23.7 & [21, 26.5] & 0.00 & 18.5 & [16.1, 21.1] & 0.00 \\ 
	Frequency & -2.9 & [-6.3, 0.5] & 0.10 & 2.9 & [-0.2, 6] & 0.06 & 0.4 & [-2.7, 3.5] & 0.79 \\ 
	Length & 20.5 & [15.4, 25.6] & 0.00 & 18.5 & [13.3, 23.7] & 0.00 & 21.4 & [16.2, 26.6] & 0.00 \\ 
	Surprisal:Length & -2.0 & [-3, -1] & 0.00 & -1.8 & [-2.7, -0.9] & 0.00 & -1.4 & [-2.2, -0.6] & 0.00 \\
	Freq:Length & -1.0 & [-2.5, 0.4] & 0.16 & -0.1 & [-1.2, 1] & 0.82 & 0.2 & [-0.9, 1.2] & 0.76 \\ 
	\hline
	Past Surprisal & 1.6 & [-0.5, 3.6] & 0.14 & 2.7 & [0.8, 4.5] & 0.00 & 0.8 & [-0.9, 2.5] & 0.40 \\ 
	Past Freq & 2.6 & [-0.1, 5.4] & 0.06 & 1.9 & [-0.2, 4.2] & 0.08 & 1.2 & [-1.1, 3.6] & 0.30 \\ 
	Past Length & -4.8 & [-9, -0.1] & 0.04 & -6.6 & [-10.9, -2.1] & 0.00 & -5.2 & [-9.3, -0.7] & 0.03 \\ 
	Past Surp:Length & -0.2 & [-1.2, 0.8] & 0.72 & -0.9 & [-1.7, -0.2] & 0.01 & -0.6 & [-1.3, 0.2] & 0.13 \\ 
	Past Freq:Length & -1.0 & [-2.3, 0.3] & 0.15 & -1.8 & [-2.9, -0.8] & 0.00 & -1.5 & [-2.6, -0.5] & 0.01 \\

	\hline
\end{tabular}
\end{tiny}
\end{frame}
